---
title: "Grassland forage quality estimation with UAV-borne hyperspectral data"
author: "Jayan Wijesingha"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  slidy_presentation:
    footer: "(C) jayan.wijesingha@uni-kassel.de"
    #css: ./stylesheets/css_slidy.css
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(data.table)
library(dplyr)
library(hsdar)
library(ggplot2)
library(caret)
library(purrr)
library(readr)
library(ppls)
library(tibble)
library(kableExtra)

windowsFonts(Helvetica=windowsFont("Helvetica-Regular"))
```

## Summary of the grasslands


```{r grassland info, echo=FALSE, results='asis'}

gl_df <- data.frame(
  field_id = c("G1a", "G1b", "G2", "G3", "BG", "BGL", "GH", "GHL"),
  area = c(rep("Werra-Meißner district", 4), rep("Biosphere Reserve Rhön", 4)),
  veg_type = c("Mountain hay meadow", "*Nardus stricta* grassland",
               "Lowland hay meadow", "Seeded grassland", 
               "*Nardus stricta* grassland", 
               "Former *Nardus stricta* grassland invaded by *Lupinus polyphyllus*",
               "Mountain hay meadow",
               "Former Mountain hay meadow invaded by *Lupinus polyphyllus*"
  )
  )

kable(gl_df, col.names = c("Field ID", "Area", "Vegetation Type")) %>%
  kable_styling(bootstrap_options = c("striped"), full_width = T)

```


## N (%) Concentration Data

```{r read df, include=FALSE}
## Read WIZ data
wiz_df <-  fread("D:/Data_Processing/2018/fq_modelling_2018/output_wiz/hs_all_nrm_df_wiz.csv", header = TRUE)
wiz_df$source <- rep("Witzenhausen", dim(wiz_df)[1])
## Read Rhön data
dsb_df <-
  read.csv("D:/Data_Processing/2018/fq_modelling_2018/output_dsb/hs_all_nrm_df_dsb.csv", header = TRUE)
dsb_df$source <- rep("Rhön", dim(dsb_df)[1])
## merging two data sets
all_df <- rbind(wiz_df, dsb_df)
all_df$doy <- factor(all_df$doy)
```

```{r Boxplot N, out.width='60%', fig.align='center'}
ggplot(all_df, aes (x = doy, y = n, fill = field_id)) + 
  geom_boxplot(alpha = 0.75) +
  theme_bw(base_size = 12, base_family = "Helvetica") +
  jcolors::scale_fill_jcolors("pal7",
                    name = "Grassland ID", 
                    labels = c("G1a", "G1b", "G2", "G3", "BG", "BGL", "GH", "GHL")) +
  labs(x = "Julian date (DOY)",
       y = "N (%) per dry matter",
       caption = "Nitrogen (N) concentration data (all)") +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.caption = element_text(size = 11, face = "italic", hjust = 1),
    legend.position = "bottom"
  )
```

## N (%) estimation with different machine learning algorithms

### Partial least squares regression (PLSR)

```{r N PLSR load, include=FALSE}
load("D:/Data_Processing/2018/fq_modelling_2018/output/models/100_times/plsr_100.RData")

source("D:/Data_Processing/2018/fq_modelling_2018/funs/obs_pred_plot.R")
```

```{r N PLSR plot, fig.align='center', out.width='50%'}
obs_pred_plot(pls_best_fit_n, pls_test_list[[pls_best_k_for_n]], 
              estimators, targetN, plot = TRUE, 
              title = "N (%) estimation model with PLSR")
rm(list = ls()[grep("pls", ls())])
```

### Random forest regression (RFR)

```{r N RFR load, include=FALSE}
load("D:/Data_Processing/2018/fq_modelling_2018/output/models/100_times/rfr_100.RData")

source("D:/Data_Processing/2018/fq_modelling_2018/funs/obs_pred_plot.R")
```

```{r N RFR plot, fig.align='center', out.width='50%'}
obs_pred_plot(rf_best_fit_n, rf_test_list[[rf_best_k_for_n]], 
              estimators, targetN, plot = TRUE, 
              title = "N (%) estimation model with RFR")
rm(list = ls()[grep("rf", ls())])
```

### Gaussian process regression (GPR)

```{r N GPR load, include=FALSE}
load("D:/Data_Processing/2018/fq_modelling_2018/output/models/100_times/gpr_100.RData")

source("D:/Data_Processing/2018/fq_modelling_2018/funs/obs_pred_plot.R")
```

```{r N GPR plot, fig.align='center', out.width='50%'}
obs_pred_plot(gp_best_fit_n, gp_test_list[[gp_best_k_for_n]], 
              estimators, targetN, plot = TRUE, 
              title = "N (%) estimation model with GPR")
rm(list = ls()[grep("gp", ls())])
```

### Support vector machine regression (SVMR)

```{r N SVMR load, include=FALSE}
load("D:/Data_Processing/2018/fq_modelling_2018/output/models/100_times/svmr_100.RData")

source("D:/Data_Processing/2018/fq_modelling_2018/funs/obs_pred_plot.R")
```

```{r N SVMR plot, fig.align='center', out.width='50%'}
obs_pred_plot(svm_best_fit_n, svm_test_list[[svm_best_k_for_n]], 
              estimators, targetN, plot = TRUE, 
              title = "N (%) estimation model with SVMR")
rm(list = ls()[grep("svm", ls())])
```

## ADF (%) Concentration Data

```{r Boxplot ADF, out.width='60%', fig.align='center'}
ggplot(all_df, aes (x = doy, y = adf, fill = field_id)) + 
  geom_boxplot(alpha = 0.75) +
  theme_bw(base_size = 12, base_family = "Helvetica") +
  jcolors::scale_fill_jcolors("pal7",
                    name = "Grassland ID", 
                    labels = c("G1a", "G1b", "G2", "G3", "BG", "BGL", "GH", "GHL")) +
  labs(x = "Julian date (DOY)",
       y = "ADF (%) per dry matter",
       caption = "Acid detergent fiber (ADF) concentration data (all)") +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.caption = element_text(size = 11, face = "italic", hjust = 1),
    legend.position = "bottom"
  )
```

## ADF (%) estimation with different machine learning algorithms

### Partial least squares regression (PLSR)

```{r ADF PLSR load, include=FALSE}
load("D:/Data_Processing/2018/fq_modelling_2018/output/models/100_times/plsr_100.RData")

source("D:/Data_Processing/2018/fq_modelling_2018/funs/obs_pred_plot.R")
```

```{r ADF PLSR plot, fig.align='center', out.width='50%'}
obs_pred_plot(pls_best_fit_adf, pls_test_list[[pls_best_k_for_adf]], 
              estimators, targetADF, plot = TRUE, 
              title = "ADF (%) estimation model with PLSR")
rm(list = ls()[grep("pls", ls())])
```

### Random forest regression (RFR)

```{r ADF RFR load, include=FALSE}
load("D:/Data_Processing/2018/fq_modelling_2018/output/models/100_times/rfr_100.RData")

source("D:/Data_Processing/2018/fq_modelling_2018/funs/obs_pred_plot.R")
```

```{r ADF RFR plot, fig.align='center', out.width='50%'}
obs_pred_plot(rf_best_fit_adf, rf_test_list[[rf_best_k_for_adf]], 
              estimators, targetADF, plot = TRUE, 
              title = "ADF (%) estimation model with RFR")
rm(list = ls()[grep("rf", ls())])
```

### Gaussian process regression (GPR)

```{r ADF GPR load, include=FALSE}
load("D:/Data_Processing/2018/fq_modelling_2018/output/models/100_times/gpr_100.RData")

source("D:/Data_Processing/2018/fq_modelling_2018/funs/obs_pred_plot.R")
```

```{r ADF GPR plot, fig.align='center', out.width='50%'}
obs_pred_plot(gp_best_fit_adf, gp_test_list[[gp_best_k_for_adf]], 
              estimators, targetADF, plot = TRUE, 
              title = "ADF (%) estimation model with GPR")
rm(list = ls()[grep("gp", ls())])
```

### Support vector machine regression (SVMR)

```{r ADF SVMR load, include=FALSE}
load("D:/Data_Processing/2018/fq_modelling_2018/output/models/100_times/svmr_100.RData")

source("D:/Data_Processing/2018/fq_modelling_2018/funs/obs_pred_plot.R")
```

```{r ADF SVMR plot, fig.align='center', out.width='50%'}
obs_pred_plot(svm_best_fit_adf, svm_test_list[[svm_best_k_for_adf]], 
              estimators, targetADF, plot = TRUE, 
              title = "ADF (%) estimation model with SVMR")
rm(list = ls()[grep("svm", ls())])
```

